Выпускная квалификационная работа

### 2025-06-02 TeX/CDAM/en_cdam_KhromovGolyandina.tex
Cites reorder
new mail

%%% Title section
\begin{center}
  {\Large\bf TENSORS FOR SIGNAL AND FREQUENCY ESTIMATION IN
  SUBSPACE-BASED METHODS: WHEN THEY ARE USEFUL?}\\\vspace{2mm} {\sc N.A.
  Khromov$^1$, N.E. Golyandina$^2$}\\\vspace{2mm}
  {\it $^{1}$ $^{2}$St.\,Petersburg State University\\
  St.\,Petersburg, Russia\\} e-mail: {\tt $^1$hromovn@mail.ru,
  $^2$n.golyandina@spbu.ru}

>>>>

%%% Title section
\begin{center}
  {\Large\bf TENSORS FOR SIGNAL AND FREQUENCY ESTIMATION IN
  SUBSPACE-BASED METHODS: WHEN THEY ARE USEFUL?}\\\vspace{2mm} {\sc N.A.
  Khromov$^1$, N.E. Golyandina$^2$}\\\vspace{2mm}
  {\it $^{1}$ $^{2}$St.\,Petersburg State University\\
  St.\,Petersburg, Russia\\} e-mail: {\tt $^1$hromovn0@gmail.com,
  $^2$n.golyandina@spbu.ru}
